Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-20 doc/GMP2015/appendix_a.tex
re-phrased the main proof once again.

\begin{proof}
Observation \ref{lemma:union_intersection} shows that the intersection of any two isostatic subgraphs (such as $C_i$ and $C_j$) can only result in trivial or isostatic subgraphs. Therefore, these are the only possibilities to consider.

\medskip\noindent
\vemph{Part 1:} We show that no subset of the children can union to form $C$, thereby requiring all of them be included, and because this is the only choice it must be optimal for this node.

Take the strict subset $S\subsetneq \{1,\ldots,N\}$ such that $U=\bigcup_{i\in S}{C_i}$ which we \vemph{assume} is isostatic. If $U\neq C$, then we just found a larger proper subgraph and the children were not vertex-maximal to begin with. So, it must be that $U=C$.
\usestwod
However, since $C_i \cap C_j$ is trivial then for $k\notin S$ we know, by Lemma \ref{lemma:combined_lemma}, point \ref{lemma:uc_intersection_makes_all_uc}, $U\cap C_k$ must be one or more trivial subgraphs. By definition of a DR-plan $C_k=C\cap C_k$ and we know that $U=C$ so $C_k=U\cap C_k$. Thus, $C_k$ is both one or more trivial subgraphs and a isostatic subgraph of $C$. Thus, the assumption is wrong and $U$ cannot be isostatic. As $C$ is isostatic, this means no proper subset of the children in ComDRP$(C)$ can union to form $C$.

\medskip\noindent
\vemph{Part 2:} If $C_i \cap C_j$ is isostatic, then, by Observation \ref{lemma:union_intersection}, $C_i \cup C_j$ is also isostatic. This means that, by Lemma \ref{lemma:combined_lemma}, point \ref{lemma:wc_intersection_makes_all_wc}, any two children of $C$ will union to $C$ itself. Thus, any two children are potential choices for the optimal DR-plan as they all create equal fan-in (exactly two) at this level.

However, to guarantee that any two are the \vemph{optimal} choice, it must ensure minimum fan-in for any descendant. Take the set $S_N=\{1,\dots,N\}$, then we call $I=\bigcap_{k\in S_N}{C_k}$ and $R_k=C\setminus C_k$. Suppose we select $i$ and $j$, where $i\neq j$, as the children. Since
\[C_i=Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i\}}{R_k}\right)\]
the children of this node will be
\[Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,m\}}{R_k}\right)\]
and
\[Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,n\}}{R_k}\right)\]
% $C_i=Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i\}}{R_k}\right)$
% the children of this node will be
% $Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,m\}}{R_k}\right)$
% and
% $Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,n\}}{R_k}\right)$
for arbitrary $m$ and $n$, where $i,j,m,n$ do not equal each other. \todo{Prove these are valid children? Or is this obvious?} This continues for $N-1$ levels total, always with fan-in of two (the minimum possible), at which point every descendant of $C$ is some $Idc(C,I\cup R_k)$ for $k\in S_N$, with every $k$ appearing at least once. Thus, regardless of the choice of $i,j$ and then $m,n$ etc., the DR-plan has fan-in of two for every node for the next $N$ levels, at which point the nodes contain the same subgraphs.

This proof then applies to itself recursively to show that the fan-in of the children will also be minimum, thereby making this the optimal DR-plan.
\end{proof}

>>>>

\begin{proof}
Observation \ref{lemma:union_intersection} shows that the intersection of any two isostatic subgraphs can only result in trivial or isostatic subgraphs. Therefore, given $C$ and its isostatic vertex-maximal subgraphs $C_1,\ldots,C_N$, the are only two possibilities to consider. Either (1) subgraphs $C_i$ and $C_j$ have a trivial intersection, or (2) they have an isostatic intersection.

\medskip\noindent
\vemph{Part 1:} First, we claim that if the intersection is trivial all $C_1,\ldots,C_N$ must be children of $C$ in a canonical DR-plan. We do this by showing that no subset of the children can union to form $C$, thereby requiring all of them be included; because this is the only choice, it is the minimum fan-in a canonical DR-plan could have for this node.
must be optimal for this node.

Take the strict subset $S\subsetneq \{1,\ldots,N\}$ such that $U=\bigcup_{i\in S}{C_i}$ which we \vemph{assume} is isostatic. If $U\neq C$, then we just found a larger proper subgraph and the children were not vertex-maximal to begin with. So, it must be that $U=C$.
\usestwod
However, since $C_i \cap C_j$ is trivial then for $k\notin S$ we know, by Lemma \ref{lemma:combined_lemma}, point \ref{lemma:uc_intersection_makes_all_uc}, $U\cap C_k$ must be one or more trivial subgraphs. By definition of a DR-plan $C_k=C\cap C_k$ and we know that $U=C$ so $C_k=U\cap C_k$. Thus, $C_k$ is both one or more trivial subgraphs and a isostatic subgraph of $C$. Thus, the assumption is wrong and $U$ cannot be isostatic. As $C$ is isostatic, this means no proper subset of $C_1,\ldots,C_N$ can union to form $C$.

Furthermore, since a canonical DR-plan uses proper rigid \vemph{vertex-maximal} subgraphs as children, and because their pairwise intersection is trivial, it follows that any such node has at most as many children as a DR-plan without this restriction, because the union of the children have to contain all edges of the parent. Therefore, this is the optimal choice in this case.

\medskip\noindent
\vemph{Part 2:} Second, we claim that if the intersection is isostatic any two children will suffice for a canonical DR-plan and that it will be optimal.

If $C_i \cap C_j$ is isostatic, then, by Observation \ref{lemma:union_intersection}, $C_i \cup C_j$ is also isostatic. This means that, by Lemma \ref{lemma:combined_lemma}, point \ref{lemma:wc_intersection_makes_all_wc}, any two children of $C$ will union to $C$ itself. Thus, any two children can be chosen to make a canonical DR-plan.
% are potential choices for the optimal DR-plan as they all create equal fan-in (exactly two) at this level.

\newcommand{\induceonc}[1]{Idc\left(C,#1\right)}
\renewcommand{\induceonc}[1]{#1}
\newcommand{\iunion}[1]{\induceonc{I\cup\bigcup_{k\in S_N\setminus\{#1\}}{R_k}}}

However, to guarantee that any two are the \vemph{optimal} choice, it must ensure minimum fan-in over all descendants. Take the set $S_N=\{1,\dots,N\}$, then we call $I=\bigcap_{k\in S_N}{C_k}$ and $R_k=C\setminus C_k$. Suppose we select $i$ and $j$, where $i\neq j$, as the children. For convenience, we will assume all subgraphs are induced subgraphs on $C$. We know that $C=\induceonc{I\cup\bigcup_{k\in S_N}{R_k}}$ and $C_i=\iunion{i}$. The isostatic vertex-maximal subgraphs of $C_i$ are $(\iunion{i,1}),\ldots,(\iunion{i,i-1}),(\iunion{i,i+1}),\ldots,(\iunion{i,N})$ all of which intersect on isostatic subgraphs. So any two of these are viable children for $C_i$.
% Since
% \[C_i=Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i\}}{R_k}\right)\]
% the children of $C_i$ will be
% \[Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,m\}}{R_k}\right)\]
% and
% \[Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,n\}}{R_k}\right)\]
% % $C_i=Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i\}}{R_k}\right)$
% % the children of this node will be
% % $Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,m\}}{R_k}\right)$
% % and
% % $Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,n\}}{R_k}\right)$
% for arbitrary $m$ and $n$, where $i,j,m,n$ do not equal each other. \todo{Prove these are valid children? Or is this obvious?}
This continues for $N-1$ levels total, always with fan-in of two (the minimum possible), at which point every descendant of $C$ is some $\induceonc{I\cup R_k}$ for $k\in S_N$, with every $k$ appearing at least once. Thus, regardless of the choice of $C_i,C_j$, then their children, etc., the DR-plan has fan-in of two for every node for the next $N$ levels, at which point the nodes contain the same subgraphs. Therefore, the choice is optimal.

\medskip\noindent
This proof then applies to itself recursively to show that the fan-in of the children will also be minimum.
\end{proof}

### 2014-12-20 doc/GMP2015/s03_drp.tex
re-phrased the main proof once again.

\begin{theorem} \label{theorem:canonical_is_optimal}
    \label{theorem:main}
    Any canonical DR-plan is an optimal DR-plan.
\end{theorem}

@@

\myexample
\textsl{[DR-Plan for self-similar structure]}
This section details the decomposition of the graph in Figure \ref{fig:c2c3ofk33s}. The graph $G$ has only two isostatic vertex-maximal subgraphs, $G$ without the outermost triangle composed of $K_{3,3}$ graphs (triangle $1$) and $G$ without the inner triangle $N$. These intersect on $G$ without triangle $1$ and $N$ which is clearly well-constrained. As explained in the proof of Theorem \ref{theorem:main}, part 2, since there are only 2 possible children, their intersection must be a node 2 levels below the parent. Just as expected, it is on the third level, as it is a child of both of $G$'s children. Furthermore, it intersects trivially with the edges that connect triangle $1$ and $N$ to $2$ and $N-1$, respectively; these necessarily intersect with triangle $1$ and $N$ themselves trivially (by Theorem \ref{theorem:main}, part 1) making all of these children. The triangles then decompose into their constituent $K_{3,3}$ graphs, which then decompose into 9 edges.

>>>>

\begin{theorem}
\label{theorem:canonical_exists_and_is_optimal}
\label{theorem:canonical_is_optimal}
\label{theorem:main}
    A canonical DR-plan exists and any canonical DR-plan is optimal.
\end{theorem}

% \begin{theorem} \label{theorem:canonical_is_optimal}
%     \label{theorem:main}
%     Any canonical DR-plan is an optimal DR-plan.
% \end{theorem}

@@

\myexample
\textsl{[DR-Plan for self-similar structure]}
This section details the decomposition of the graph in Figure \ref{fig:c2c3ofk33s}. The graph $G$ has only two isostatic vertex-maximal subgraphs, $G$ without the outermost triangle composed of $K_{3,3}$ graphs (triangle $1$) and $G$ without the inner triangle $N$. These intersect on $G$ without triangle $1$ and $N$ which is clearly well-constrained. As explained in the proof of Theorem \ref{theorem:main} since there are only 2 possible children, their intersection must be a node 2 levels below the parent. Just as expected, it is on the third level, as it is a child of both of $G$'s children. Furthermore, it intersects trivially with the edges that connect triangle $1$ and $N$ to $2$ and $N-1$, respectively; these necessarily intersect with triangle $1$ and $N$ themselves trivially (by Theorem \ref{theorem:main}, part 1) making all of these children. The triangles then decompose into their constituent $K_{3,3}$ graphs, which then decompose into 9 edges.

### 2014-12-20 doc/GMP2015/s07_problempinning.tex
re-phrased the main proof once again.

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.35\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
%
\caption{(a) is a 1-dof body-pin graph. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}
%
\end{figure*}
The above discussion leads to the main theorem:
\begin{theorem}
\label{thm:1dofcase}
    Given a 1-dof body-pin or triangle-multipin graph $G$ and corresponding
    1-dof DR-plan $T$, there is an \candrpcomplexity algorithm for the 1-dof optimal
    completion problem of Section \ref{sec:recomb}.
\end{theorem}

>>>>

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.35\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
%
\caption{(a) is a 1-dof body-pin graph. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}
%
\end{figure*}
The above discussion leads to the main theorem:
\begin{theorem}
\label{thm:1dofcase}
    Given a 1-dof body-pin or triangle-multipin graph $G$ and corresponding
    1-dof DR-plan $T$, there is a quadratic algorithm for the 1-dof optimal
    completion problem of Section \ref{sec:recomb}.
\end{theorem}
